OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-03-05 paper/paper.Rmd
'as fast as' vs 'slower than'

```{r de_novo}
dn_vsearch_mcc <- dat %>% filter(strategy == 'de_novo', tool == 'vsearch') %>% pull(mcc_median) %>% median()
dn_vsearch_sec <- dat %>% filter(strategy == 'de_novo', tool == 'vsearch') %>% pull(sec_median) %>% median()
mcc_opticlust_vs_vsearch <- rel_diff(opticlust_mcc, dn_vsearch_mcc)
sec_opticlust_vs_vsearch <- rel_diff(opticlust_sec, dn_vsearch_sec)
```

@@

In open reference mode, fitting the datasets to reference OTUs with OptiFit
produced OTUs of similar quality (`r mcc_open_fit_db_vs_clust`% difference in median
MCC) as clustering the datasets _de novo_ with OptiClust  across all datasets
and reference databases.
OptiFit produced higher quality OTUs than VSEARCH when open reference clustering
against the Greengenes database, with median MCC scores of `r open_fit_gg_mcc`
and `r open_vsearch_mcc` (respectively).
However, OptiClust and VSEARCH each ran `r sec_opticlust_vs_open_fit_db`% and 
`r sec_vsearch_vs_open_fit_db`% faster than OptiFit in open reference mode.
_De novo_ clustering with OptiClust produced `r mcc_opticlust_vs_vsearch`%
higher quality OTUs than VSEARCH, but performed `r sec_opticlust_vs_vsearch`%
slower than VSEARCH.

>>>>

```{r de_novo}
dn_vsearch_mcc <- dat %>% filter(strategy == 'de_novo', tool == 'vsearch') %>% pull(mcc_median) %>% median()
dn_vsearch_sec <- dat %>% filter(strategy == 'de_novo', tool == 'vsearch') %>% pull(sec_median) %>% median()
mcc_opticlust_vs_vsearch <- rel_diff(opticlust_mcc, dn_vsearch_mcc)
sec_opticlust_vs_vsearch <- abs(rel_diff(dn_vsearch_sec, opticlust_sec))
```

@@

In open reference mode, fitting the datasets to reference OTUs with OptiFit
produced OTUs of similar quality (`r mcc_open_fit_db_vs_clust`% difference in median
MCC) as clustering the datasets _de novo_ with OptiClust  across all datasets
and reference databases.
OptiFit produced higher quality OTUs than VSEARCH when open reference clustering
against the Greengenes database, with median MCC scores of `r open_fit_gg_mcc`
and `r open_vsearch_mcc` (respectively).
However, OptiClust and VSEARCH each ran `r sec_opticlust_vs_open_fit_db`% and 
`r sec_vsearch_vs_open_fit_db`% faster than OptiFit in open reference mode.
_De novo_ clustering with OptiClust produced `r mcc_opticlust_vs_vsearch`%
higher quality OTUs than VSEARCH, but performed only 
`r sec_opticlust_vs_vsearch`% as fast as VSEARCH.
